### 2021-04-21 Chapter-5/Chapter-5.tex
Updates from Overleaf

\section{Evaluation}
In this section, we evaluate \ctool{} on several small benchmarks and real-world software trying to answer the following questions:

@@

\textit{Small Programs:} We use two benchmarks that are well studied in the previous work. The amount of actual leakage of those samples are known. We use them to evaluate the precision of the tool.

@@

\begin{table}
\footnotesize
\caption{Evaluation results overview: Name of the benchmark, The Size of the Input Data, The number of leaked functions, The Maximum Leakage, The size of the benchmark, and Performance.}\label{chapter5:table:over_result}
\centering
\resizebox{\columnwidth}{!}{
\begin{tabular}{lrrrrrrrrrrr}\toprule

@@

>>>>

\section{Evaluation}
In this section, we evaluate \ctool{} on real-world software trying to answer the following questions:

@@

@@

\begin{sidewaystable}
\footnotesize
\caption{Evaluation results overview: Name of the benchmark, The Size of the Input Data, The number of leaked functions, The Maximum Leakage, The size of the benchmark, and Performance.}\label{chapter5:table:over_result}
\centering
\resizebox{\columnwidth}{!}{
\begin{tabular}{lrrrrrrrrrrr}\toprule

@@

\end{sidewaystable}
